|

### 2022-02-26 paper/dcpo_demsupport.Rmd
citation updated, #36

- Yuehong 'Cassandra' Tai, Ph.D. Candidate, Department of Political Science, University of Iowa, yuehong-tai@uiowa.edu.
- Yue Hu, corresponding author, ORCID: https://orcid.org/0000-0002-2829-3971, Associate Professor, Department of Political Science, Tsinghua University, yuehu@tsinghua.edu.cn
- Frederick Solt, ORCID: https://orcid.org/0000-0002-3154-6132, Associate Professor, Department of Political Science, University of Iowa, frederick-solt@uiowa.edu."

@@

The three authors contributed equally to this work. 
We thank the editors and anonymous reviewers for their helpful comments. 
All errors remain our own.

@@

# load all the packages you will use below
p_load(
    # analysis
    plm,

@@

    # data wrangling
    here,
    broom,
    tidyverse,
    glue)

@@

```{r compare_n}

# if (!file.exists(here::here("data", "supdem raw survey marginals.tab"))) {
#   dataverse::get_file("supdem raw survey marginals.tab", "doi:10.7910/DVN/HWLW0J") %>% 
#     read_csv(col_types = "cdcddcdc") %>% 
#     write_csv("data/supdem raw survey marginals.tab")
# }

supdem <- read_csv(here::here("data", "supdem raw survey marginals.tab"),
                   col_types = "cdcddcdc") %>% 
  janitor::clean_names() %>% 
  DCPOtools::with_min_yrs(2)

@@

```{r pointAJPS}
supdem <- read.csv(here("data", "Support_democracy_ajps.csv"))
sd.plm <- pdata.frame(supdem, index = c("Country", "Year"))

@@

```{r pointAPSR}
# Reusing the sd.plm object, thus input data here rather than earlier

@@

Research documentation and data that support the findings of this study are openly available in the APSR Dataverse at [DOI].

>>>>

- Yuehong 'Cassandra' Tai, ORCID: https://orcid.org/0000-0001-7303-7443, Ph.D. Candidate, Department of Political Science, University of Iowa, yuehong-tai@uiowa.edu.
- Yue Hu, corresponding author, ORCID: https://orcid.org/0000-0002-2829-3971, Associate Professor, Department of Political Science, Tsinghua University, yuehu@tsinghua.edu.cn
- Frederick Solt, ORCID: https://orcid.org/0000-0002-3154-6132, Associate Professor, Department of Political Science, University of Iowa, frederick-solt@uiowa.edu.

@@

The three authors contributed equally to this work. 
We thank the editors and anonymous reviewers for their helpful comments.
All errors remain our own.
Replication files are available at the American Political
Science Review Dataverse: https://doi.org/XXXX.

@@

# load all the packages you will use below
p_load(
    # data
    dataverse,

    # analysis
    plm,

@@

    # wrangling
    here,
    broom,
    tidyverse,
    glue)

Sys.setenv("DATAVERSE_SERVER" = "dataverse.harvard.edu")

@@

```{r compare_n}
if (!file.exists(here("data", "supdem raw survey marginals.tab"))) {
  dataverse::get_file("supdem raw survey marginals.tab", "doi:10.7910/DVN/HWLW0J") %>%
    read_csv(col_types = "cdcddcdc") %>%
    write_csv("data/supdem raw survey marginals.tab")
}

supdem <- read_csv(here("data", "supdem raw survey marginals.tab"),
                   col_types = "cdcddcdc") %>% 
  janitor::clean_names() %>% 
  DCPOtools::with_min_yrs(2)

@@

```{r pointAJPS}
if (!file.exists(here("data", "Support_democracy_ajps.csv"))) {
  get_file_by_doi(filedoi = "10.7910/DVN/HWLW0J/MVXNFC") %>%
    read_csv(col_types = "cdcddcdc") %>%
    write_csv(here("data", "Support_democracy_ajps.csv"))
}

supdem <- read.csv(here("data", "Support_democracy_ajps.csv"))
sd.plm <- pdata.frame(supdem, index = c("Country", "Year"))

@@

```{r pointAPSR}
# Reusing the sd.plm object, thus input data here rather than earlier
if (!file.exists(here("data", "dem_mood_apsr.RData"))) {
  get_dataframe_by_doi(filedoi = "10.7910/DVN/FECIO3/ACMGQG") %>%
    save(file = here("data", "dem_mood_apsr.RData"))
}

@@

Research documentation and data that support the findings of this study are openly available in the APSR Dataverse at https://doi.org/XXXX.
